---
title: "HW2Part1"
author: "Yang Ge"
date: "October 8, 2015"
output: 
  html_document:
    keep_md: true
    toc: true
---

```{r setoptions, echo=TRUE}
library(knitr)
opts_chunk$set(echo = TRUE, cache = TRUE)
```

# Problem 1

$$
Pr(h\ \text{makes mistakes}) = Pr(y=f(x) \cap h(x) \ne f(x)) + Pr(y \ne f(x) \cap h(x) = f(x))
= \lambda\mu + (1-\lambda)(1-\mu)
$$

# Problem 2

if $\lambda = 0.5$, above equation becomes a constant 0.5.

# Problem 3

```{r, echo=TRUE, cache=TRUE}
sample.size <- c(480000, 440000, 500000, 420000, 460000)
delta <- 0.05
epsilon <- 0.05
dvc <- 10
compute.gen.error <- function(N) {
    sqrt(8/N * log(4*(2*N)^dvc / delta) )
}
gen.error <- sapply(sample.size, compute.gen.error)
gen.error
gen.error.diff <- abs(gen.error - epsilon)
q3.ans <- sample.size[which.min(gen.error.diff)]
q3.ans
```

The above code show the anwser should be `r q3.ans`

# Problem 4
```{r}
data.size <- seq(1000, 10000, 1000)
dvc <- 50
delta <- 0.05
N <- 10000
vcbound <- function(N) {
    sqrt(8/N * log(4*(2*N)^dvc / delta) )
}
rademacher <- function(N) {
    sqrt(2/N * log(2*N*(N)^dvc)) + sqrt(2/N*log(1/delta)) + 1/N 
}
vcvariant <- function(N) {
    sqrt(16/N*log(2*(N)^dvc/sqrt(delta)))
}
parrondo <- function(N, e) {
    sqrt(1/N *( 2*e + log(6*(2*N)^dvc/delta) ))
}
devroye <- function(N, e) {
    sqrt( 1 / (2*N) * (4*e*(1+e) + ( log(4) + 2*dvc*log(N) - log(delta) ) ) )
}
print("vcbound when N = 10000:")
vcbound(N)
rademacher(N)
vcvariant(N)
parrondo(N, 0.2237)
devroye(N, 0.215228)
```

The above code show the anwser should be Parrondo.

# Problem 5
```{r}
N <- 5
vcbound(N)
rademacher(N)
vcvariant(N)
parrondo(N, 5.101363)
devroye(N, 5.593126)
```

The above code show the anwser should still be Parrondo.

# Problem 6

We select 2 slots among first $N$ slots and then plus 2 all -1 and all +1 cases.
So it's $2\times\binom{N}{2}+2 = N^2 - N + 2$

# Problem 7

Then the VC dimension is 3. When $N = 4$, it cannot be shattered.

# Problem 8

Just consider rotating all points to the x-axis, then it's equivalent to positive interval.
So it is:
$$
m_{\mathcal{H}}(N) = \binom{N+1}{2} + 1 = \frac{N^2}{2} + \frac{N}{2} + 1 \ll 2^N
$$

# Problem 9

Polynomial with degree $D$ can have up to $D$ roots, so as long as we arrange the roots
according to the data points, we can shatter $D+1$ points. Which means the VC dimension is $D+1$.
For example, say, $D=2$, we can shatter 3 points.

# Problem 10

The notation is confusing, $t$ is fixed for one hypothesis, \boldmath$S$\unboldmath is also fixed for one
hypothesis. Let me assume $d = 2$, then for a given t, the 2-D plane is divided into 4 parts. If there are
5 data points, then at least two of them will be in the same parts. And it cannot be shattered.
So I think the VC dimension is $2^d$.

# Problem 11

It's like we have an infinity $D$ in problem 9, so the answer is $\infty$

# Problem 12

Because we have the following equations, so my intuition is that none of them is right.

$$
m_{\mathcal{H}}(N) \leq N^{d_{VC}}, if N \geq 2, d_{VC} \geq 2
$$

But the answer turned out to be

$$
\overset{min}{1\leq i \leq N-1} 2^i m_{\mathcal{H}}(N-i)
$$

# Problem 13

Don't know yet. But the answer is $N$

# Problem 14

It's easy. First, the intersection can be empty set, so the left will be $0\leq$.
The right side is also obvious.

# Problem 15

The left hand side is easy. But I don't understand the right side

$$
K-1 + \sum_{k=1}^{K} d_{vc}(\mathcal{H})
$$

# Problem 16

Just need to consider when $\theta = 0$, if $s = 1$, then we have 80% chance to predict right.
If $s = -1$, then we only have 20% chance to predict right, So then answer should be the following.
Note that it asks $E_{out}$

$$
0.5 + 0.3s(|\theta| - 1)
$$