---
title: "HW4Part2"
author: "Yang Ge"
date: "November 5, 2015"
output:
  html_document:
    keep_md: true
    toc: true
---

```{r setoptions, echo=TRUE}
library(knitr)
opts_chunk$set(echo = TRUE, cache = TRUE)
library(dplyr)
```

# Problem 13

```{r problem13}
setwd("C:/Users/YANGGE/Documents/GitHub/MachineLearningProfLin/MachineLearningFoundation/HW4/")
dat.trn <- read.table("ntumlone-hw4-hw4_train.dat")
dat.tst <- read.table("ntumlone-hw4-hw4_test.dat")

# Preprocess the data
lambda <- 10.0
d <- ncol(dat.trn)
N <- nrow(dat.trn)
x.trn <- as.matrix(cbind(rep(1, N), dat.trn[, 1:d-1]))
y.trn <- dat.trn[, d]
x.tst <- as.matrix(cbind(rep(1, N), dat.tst[, 1:d-1]))
y.tst <- dat.tst[, d]

w.reg <- solve(t(x.trn) %*% x.trn + lambda*diag(d), t(x.trn) %*% y.trn)

y.trn.pred <- sign(x.trn %*% w.reg)
err.trn <- sum(y.trn != y.trn.pred) / N

y.tst.pred <- sign(x.tst %*% w.reg)
err.tst <- sum(y.tst != y.tst.pred) / nrow(x.tst)
```

From the above code, we know $E_{in} =$ `r err.trn`. And $E_{out} =$ `r err.tst`.

# Problem 14

```{r problem14}
lambda.vector <- 10^c(2:-10)
error.frame <- data.frame(lambda=double(), ein=double(), eout=double())
nrow(error.frame)
for (lambda in lambda.vector) {
    w.reg <- solve(t(x.trn) %*% x.trn + lambda*diag(d), t(x.trn) %*% y.trn)

    y.trn.pred <- sign(x.trn %*% w.reg)
    err.trn <- sum(y.trn != y.trn.pred) / N

    y.tst.pred <- sign(x.tst %*% w.reg)
    err.tst <- sum(y.tst != y.tst.pred) / nrow(x.tst)

    res <- data.frame(lambda = lambda, ein = err.trn, eout = err.tst)
    if (nrow(error.frame) == 0) {
        error.frame <- as.data.frame(res)
    } else {
        error.frame <- rbind(error.frame, res)
    }
}
print(error.frame)
```

From the above code, we know when $lambda = 10^8$, we have $E_{in} = 0.015$.

# Problem 15

From the above code, we know when $lambda = 10^{-7}$, we have $E_{out} = 0.015$.

# Problem 16

```{r problem16}

# Split the training and validation set
x.trn <- as.matrix(cbind(rep(1, N), dat.trn[, 1:d-1]))
y.trn <- dat.trn[, d]

x.val <- x.trn[-c(1:120),]
y.val <- y.trn[-c(1:120)]

x.trn <- x.trn[c(1:120),]
y.trn <- y.trn[c(1:120)]

error.frame <- data.frame(lambda=double(), ein=double(), eout=double(), eval = double())
for (lambda in lambda.vector) {
    w.reg <- solve(t(x.trn) %*% x.trn + lambda*diag(d), t(x.trn) %*% y.trn)

    y.trn.pred <- sign(x.trn %*% w.reg)
    err.trn <- sum(y.trn != y.trn.pred) / nrow(x.trn)

    y.val.pred <- sign(x.val %*% w.reg)
    err.val <- sum(y.val != y.val.pred) / nrow(x.val)

    y.tst.pred <- sign(x.tst %*% w.reg)
    err.tst <- sum(y.tst != y.tst.pred) / nrow(x.tst)

    res <- data.frame(lambda = lambda, ein = err.trn, eout = err.tst, eval = err.val)
    if (nrow(error.frame) == 0) {
        error.frame <- as.data.frame(res)
    } else {
        error.frame <- rbind(error.frame, res)
    }
}

print(error.frame[11,])
```

When $\lambda = 1^{-8}$, we have $E_{in} = 0$

# Problem 17

When $\lambda = 1$, we have $E_{val} = 0.0375$

# Problem 18

Take $\lambda = 1$, we have $E_{in} = 0.035$ and $E_{out} = 0.020$

# Problem 19

```{r problem19}

lambda.vector <- 10^c(2:-10)
error.frame <- data.frame(cv=integer(), lambda=double(), ein=double(), eout=double(), eval = double())

for (cv in 0:4) {
    # Split the training and validation set
    x.trn <- as.matrix(cbind(rep(1, N), dat.trn[, 1:d-1]))
    y.trn <- dat.trn[, d]
    
    x.val <- x.trn[seq((cv*40+1), (cv+1)*40),]
    y.val <- y.trn[seq((cv*40+1), (cv+1)*40)]
    
    x.trn <- x.trn[-seq((cv*40+1), (cv+1)*40),]
    y.trn <- y.trn[-seq((cv*40+1), (cv+1)*40)]
    
    for (lambda in lambda.vector) {
        w.reg <- solve(t(x.trn) %*% x.trn + lambda*diag(d), t(x.trn) %*% y.trn)
    
        y.trn.pred <- sign(x.trn %*% w.reg)
        err.trn <- sum(y.trn != y.trn.pred) / nrow(x.trn)
    
        y.val.pred <- sign(x.val %*% w.reg)
        err.val <- sum(y.val != y.val.pred) / nrow(x.val)
    
        y.tst.pred <- sign(x.tst %*% w.reg)
        err.tst <- sum(y.tst != y.tst.pred) / nrow(x.tst)
    
        res <- data.frame(cv = cv, lambda = lambda, ein = err.trn, eout = err.tst, eval = err.val)
        if (nrow(error.frame) == 0) {
            error.frame <- as.data.frame(res)
        } else {
            error.frame <- rbind(error.frame, res)
        }
    }
}

error.frame.cv <- error.frame %>% group_by(lambda) %>% summarise(avg = mean(eval))

print(error.frame.cv)
```

From above code, we know $E_{cv} = 0.03$ when $\lambda = 1^{-8}$

# Problem 20

From problem 20 and problem 14, we know $E_{in} = 0.015$ when $\lambda = 1^{-8}$. And $E_{out} = 0.020$.