---
title: "HW3Part1"
author: "Yang Ge"
date: "October 28, 2015"
output:
  html_document:
    keep_md: true
    toc: true
---

```{r setoptions, echo=TRUE}
library(knitr)
opts_chunk$set(echo = TRUE, cache = TRUE)
```

# Problem 1

```{r problem1}
N <- c(10, 25, 100, 500, 1000)
expected.ein <- function(N) {
  sigma <- 0.1
  d <- 8
  sigma^2 * (1 - (d+1)/N)
}
ein <- sapply(N, expected.ein)
ein
```

From above resutls, we know $N$ should be `r 100`.

# Problem 2

See the discussion [here](https://class.coursera.org/ntumlone-003/forum/thread?thread_id=158)
And the notes [here](http://www.stat.ucla.edu/~cocteau/stat201b/lectures/lecture3.pdf)
about hat matrix.

* a) not correct, because the eigen value are not always positive
* b) wrong, for the same reason
* c) wrong, see the links above
* d) correct, in lecture notes, we have $\text{trace}(I-H) = N - (d+1)$.
  Which means $\text{trace}(H) = (d+1)$
* e) wrong, we have $H^2 = (X(X^TX)^{-1}X^T)^2 = XX^T$. So $H^{1126} = H^2 \ne H$.

Conclusion is "none of the other choices"

# Problem 3

* $err(w) = \text{max}(0, -y w^T x)$
    * when $y = 1$, $err(w) = \text{max}(0, -s)$. When $-1 < s < 0$, $err(w) < 1$
      it's not an upper bound for 0/1 error.
* $err(w) = (\text{max}(0, 1 - y w^T x))^2$
    * when $y = -1$, $err(w) = (\text{max}(0, 1+s))^2$. It's an valid upper
      bound for 0/1 error.
    * when $y = 1$, $err(w) = (\text{max}(0, 1-s))^2$. It's an valid upper
      bound for 0/1 error.
* $err(w) = -y w^T x$
    * when $y = 1$, $err(w) = -s$. When $-1 < s < 0$, $err(w) < 1$
      it's not an upper bound for 0/1 error.
* $err(w) = \theta(-y w^T x)$
    * when $y = 1$, $err(w) = \theta(-s)$. When $-\infty < s < 0$, $err(w) < 1$
      it's not an upper bound for 0/1 error.

In conclusion, $err(w) = (\text{max}(0, 1 - y w^T x))^2$ is a valid upper bound.

# Problem 4

Following the discussion in problem 3, only $err(w) = \text{max}(0, -y w^T x)$ is
not everywhere-differentiable function of $w$.

# Problem 5

* $err(w) = \text{max}(0, -y w^T x)$
    * when $y = 1$, $err(w) = \text{max}(0, -s)$. When $s < 0$, $err(w) = -s = - w^T x$.
      Then $\nabla err(w) = -x = -yx$. $w_{t+1} \leftarrow w_{t} - \nabla err(w) = w_{t} + yx = w_{t} + [y \ne \text{sign}(s)]yx$
    * when $y = 1$, $err(w) = \text{max}(0, -s)$. When $s >= 0$, $err(w) = 0$.
      Then $\nabla err(w) = 0$. $w_{t+1} \leftarrow w_{t} - \nabla err(w) = w_{t} + 0 = w_{t} + [y \ne \text{sign}(s)]yx$

In conclusion, $err(w) = \text{max}(0, -y w^T x)$ results in PLA.

# Problem 6

$$
\nabla E(u, v) = (
  e^u + ve^{uv} + 2u - 2v - 3,
  2e^{2v} + ue^{uv} - 2u + 4v - 2
  )
$$

$$
\nabla E(0, 0) = (
1 - 3,
2 - 2
) = (-2, 0)
$$

# Problem 7

```{r problem 7}
prob7.nabla <- function(u, v) {
  u.next <- exp(u) + v*exp(u*v) + 2*u - 2*v - 3
  v.next <- 2*exp(2*v) + u*exp(u*v) - 2*u + 4*v - 2
  c(u.next, v.next)
}
prob7.E <- function(u, v) {
    exp(u) + exp(2*v) + exp(u*v) + u^2 - 2*u*v + 2*v^2 - 3*u - 2*v
}
w <- c(0, 0)
for (i in 1:5) {
  w = w - 0.01 * prob7.nabla(w[1], w[2])
  print(w)
}
prob7.E(w[1], w[2])
```

From the above, the answer should be 2.825

# Problem 8

$$
b_{uu} = e^u + v^2e{uv} + 2
$$

$$
b_{vv} = 4*e{2v} + u^2e{uv} + 4
$$

$$
b_{uv} = e^{uv} + uve^{uv} - 2
$$

So the answer is $(3,8,-1,-2,0,3)$.

# Problem 9

$$
\frac{\partial E^{2}(\Delta u, \Delta v)}{\partial \Delta u}
= 2b_{uu} \Delta u + 2 b_{uv} \Delta v + b_u
$$

$$
\frac{\partial E^{2}(\Delta u, \Delta v)}{\partial \Delta v}
= 2b_{vv} \Delta v + 2 b_{uv} \Delta u + b_v
$$

Set the above 2 to 0, we have Newton direction is $-(\nabla^2E(u,v))^{-1} \nabla E(u,v)$

# Problem 10

```{r problem10}
prob10.hessian <- function(u, v) {
  buu <- exp(u) + v^2 * exp(u*v) + 2
  bvv <- 4*exp(2*v) + u^2 * exp(u*v) + 4
  buv <- exp(u*v) + u*v * exp(u*v) - 2
  matrix(c(buu, buv, buv, bvv), nrow = 2, ncol = 2)
}
w <- c(0, 0)
for (i in 1:5) {
    hessian <- prob10.hessian(w[1], w[2])
    newtow <- solve(hessian, prob7.nabla(w[1], w[2]))
    w <- w - newtow
    # print(hessian)
    print(w)
}
prob7.E(w[1], w[2])
```

Based on above discussion, the answer is 2.361.

# Problem 11

```{r problem11}
plot(1, 1, type = "p", col = "red", xlab = "x", ylab = "y", xlim = c(-2, 2), ylim = c(-2, 2))
points(1, -1, col = "red")
points(-1, -1, col = "red")
points(-1, 1, col = "red")
points(0, 0, col = "red")
points(1, 0, col = "red")
```

From the above figure, we know the six points can be shattered.
Plus, in the lecture, we know the VC dimension should be $\tilde{d} + 1$.

# Problem 12

I think it should be $\infty$. Note that $N$ is not fixed.
